### 2015-08-13 abstract.tex
abstract word file and update

This project explores the use of application level knowledge to reduce the
time to insight for a workload (not just a single application) in a
multi-user environment where storage and other resources are shared among
users. Our approach is based on the notion of selectable data quality to
enable a tradeoff between result accuracy and near-real-time data movement
requirements for oversubscribed computational and storage resources. For the
past several decades, extreme scale computational science has been conducted
on dedicated computational and storage resources. Shared resources were
overprovisioned resulting in little or no impact from resource contention.
This changed recently. Execution times for scientific applications vary
dramatically depending on external contention for shared resources. This
execution time variance is particularly challenging in light of new usage
models that have near-real-time requirements, e.g., providing information
needed to control an experimental instrument like the Spallation Neutron
Source.

More specifically, we will explore the resource contention issues
with spreading a single data set horizontally across a single tier in the
storage hierarchy, such as spinning media, as well as vertically across
different kinds of storage media, including non-volatile memory. To manage
the varying storage media capacities and bandwidths, we provide mechanisms
to express the required data quality and the near real-time requirements of
the application. Our thesis is that by adding application level knowledge
about data to guide storage system behaviors, we obtain substantial benefits
in the organization, storage, and access to extreme scale data resulting in
improved productivity for computational science. We will demonstrate novel
techniques to facilitate efficient and effective data placement onto
multiple storage tiers and enable application-guided data reductions and
transformations to address capacity and bandwidth bottlenecks. Our goal is
to address the associated data management challenges in the context of
current and emerging storage landscapes and expedite insights into mission
critical scientific processes

>>>>

This project explores the use of application level knowledge to optimize the
times to insight across a workload of multiple applications in a multi-user
environment with shared storage and network resources. The basis for this
work is the notion of selectable data quality to explore the tradeoffs
between accuracy of results, resource requirements, and time to insight on
systems with shared, oversubscribed computational and storage resources. 
In the last several years extreme scale computational science was conducted
using dedicated computational resources, with shared resources, such as
network and storage, being overprovisioned. This resulted in little to no
impact from resource contention. The increased scale of recent, and incoming
future systems, has placed a greater emphasis on mitigating contention.

Our thesis is that by adding application level knowledge
about data to guide storage system behaviors, we will obtain substantial benefits
in the organization, storage, and access to extreme scale data resulting in
improved productivity for computational science. We will demonstrate novel
techniques to facilitate efficient and effective data placement onto
multiple storage tiers and enable application-guided data reductions and
transformations to address capacity and bandwidth bottlenecks. Our goal is
to address the associated data management challenges in the context of
current and emerging storage landscapes and expedite insights into mission
critical scientific processes.
